A new tidy data structure to support exploration and modeling of temporal data

### 2019-01-19 main.Rmd
done with key

The "key" specification contributes to creating a tsibble alongside the index. The concept of "key" is introduced to uniquely identify units or subjects that are observed over time in a data table, which is similar to a primary key [@codd_relational_1970] defining each observation in a relational database. In the wide format, each column holds a series of values, so that the column itself serves for the sake of identification. In the long format, all column names are melt to the corresponding "key" values. But the "key" is much more flexible than simply column names. Because it is not constrained to a single field, but can be comprised of multiple fields. The identifying variables that the "key" is constituted of, stay the same as they are in the original table, with no further tweaks.

Each tsibble must hold a "key". It is normally a priori known by analysts. For example, Table \ref{tab:tb-sub} describes the number of tuberculosis cases for each gender across the countries every year. This data description suggests that columns `gender` and `country` have to be declared as the key, similar to a panel variable for longitudinal data. Lacking in either of two will be inadequate for the key and thus fail to construct a tsibble. The alternative specification of the key is to include a third variable `continent`. Since `country` is nested within `continent`, it is a free variable for use. But this variable brings additional information that can be used for forecasting reconciliation [@fpp]. The key is explicit when multiple units exist in the data. Key can be implicit when it finds a univariate series in the table, but it cannot be absent from a tsibble.

Not only pinpoints a "key" observational units in the tsibble but also provides a solution to seamlessly link between the data, models, and forecasts. This neatly decouples the data from models and forecasts, leaving more room for compulsory model components, such as coefficients, fitted values and residuals. More details are given in the following section.

>>>>

The "key" specification is the second essential ingrdient for a tsibble. The "key"  introduced uniquely identifies observations that are recorded over time in a data table. It is similar to a primary key [@codd_relational_1970] defining each observation in a relational database. In the wide format, that multiple time series are often structured in, the columns hold a series of values, so that the column implicitly serves as identification. In long format, columns are melted with names converted to "key" values. However, the "key" provides much more flexibility. It is not constrained to a single field, but can be composed from multiple fields. The identifying variables that the "key" is constituted from, remain the same as in the original table, with no further tweaks.

The "key" is usually known a priori by analysts. For example, Table \ref{tab:tb-sub} describes the number of tuberculosis cases for each gender across the countries every year. This data description suggests that columns `gender` and `country` have to be declared as the key, similar to a panel variable for longitudinal data. Lacking either of two will be inadequate, because the observations are not uniquely identified, and thus will generate a tsibble construction fail. An alternative specification of the key for this data is to include a third variable `continent`. Since `country` is nested within `continent`, it is a free variable for use. This variable brings additional information that can be used for forecasting reconciliation [@fpp]. The key needs to be explicit when multiple units exist in the data. The key can be implicit when it finds a univariate series in the table, but it cannot be absent from a tsibble.

The "key" also provides a solution to link between the data, models, and forecasts. This neatly decouples the data from models and forecasts, leaving more room for necessary model components, such as coefficients, fitted values and residuals. More details are given in the following section.
